An Integration of Multiple Constraints in ACG

### 2013-07-16 lenls/abstract.tex
Some small refactoring...

G-ACG extrinsic languages correspond to ACG object languages with
intersection. More formally, it can be said that ACG object languages
are just ACG abstract languages closed on transformation by a lexicon
and we then show that G-ACG extrinsic languages are just ACG abstract
languages closed on transformation by a lexicon and intersection.

@@

However, extrinsic languages turn out to give counter-intuitive
interpretations to some graphical ACGs and we turn to another paradigm.

In the new paradigm, we interpret the nodes of the graph as terms and
the edges with statements that one term is mapped into another using a
lexicon. This leads us to the definition of the \emph{pangraphical}
language of a node $u$ in a G-ACG $\mathcal{G}$.

@@

Finally, we construct a G-ACG which integrates the French negation
constraint discussed in Section~\ref{sec:constraints}, the constraints
on extraction introduced in \cite{pogodalla2012controlling} and a
constraint handling agreement in a single grammar specification. The
negation constraint is implemented exactly as was described in
Section~\ref{sec:constraints} and the extraction constraints are taken
``as is'' from \cite{pogodalla2012controlling}. The underlying syntactic
signature is defined without any concern for the additional constraints
and the syntax-semantics signature is kept simple as well.

>>>>

G-ACG extrinsic languages correspond to ACG object languages with
intersection. More formally, it can be said that ACG object languages are just
ACG abstract languages closed on transformation by a lexicon, and we then show
that G-ACG extrinsic languages are just ACG abstract languages closed on
transformation by a lexicon and intersection.

@@

However, the extrinsic languages we have defined above turn out to give
counter-intuitive interpretations to some graphical ACGs and we revisit the
question in an another paradigm.

In the new paradigm, we interpret the nodes of the graph as terms and the
edges as statements that one term is mapped into another using a lexicon. This
leads us to the definition of the \emph{pangraphical} language of a node $u$
in a G-ACG $\mathcal{G}$.

@@

Finally, we construct a G-ACG which integrates the French negation
constraint discussed in Section~\ref{sec:constraints}, the constraints
on extraction introduced in \cite{pogodalla2012controlling} and a
constraint handling agreement in a single grammar specification. The
negation constraint is implemented exactly as was described in
Section~\ref{sec:constraints} and the extraction constraints are taken
``as is'' from \cite{pogodalla2012controlling}. The underlying syntactic
signature is defined without any concern for the additional constraints
and the syntax-semantics interface is kept simple as well.
